---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sglasso

<!-- badges: start -->
![GitHub version](https://img.shields.io/github/v/tag/byuzbasi/sglasso?label=version)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

This package provides functions for computing a group-wise variable selection method, called Scaled Group Lasso (SGLASSO), in the presence of correlations among groups. The package accompanies the article "Collinear Groupwise Selection via Scaled Group Lasso," accepted for publication in *The American Statistician*.

## Installation

You can install the development version of sglasso like so:

``` r
# install from GitHub
install.packages("devtools") # if you have not installed "devtools" package
devtools::install_github("byuzbasi/sglasso")
```

If you see a gfortran-related error, refer to the [gfortran installation guide](https://byuzbasi.github.io/sglasso/help/gfortran_installation_guide.html) to fix it.

## Screening rules

`sglasso()` includes optional screening rules through the `screen` argument:
`"SSR"`, `"SSR_fast"`, and `"none"`. The SSR rule accounts for the shifted
ridge component in the SGLASSO penalty. Screening rules
are most useful for large-scale problems with many inactive groups. For small or
moderate problems, `screen = "none"` may be equally fast or faster because it
avoids screening overhead while the final KKT checks still enforce the fitted
solution. The `SSR_fast` option is experimental and delays rest-set KKT
checks to study the speed-accuracy trade-off.


## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(sglasso)
data(GenAtHum,package = "sglasso")
X <- GenAtHum$X
y <- GenAtHum$y
group <- GenAtHum$group
n =  nrow(X)
p =  ncol(X)
set.seed(2025)
model_CV <- cv.sglasso(X,y,group, nlambda=20, nd= 5, nfold = 5, alpha = 0.4)
plot(model_CV)
plot(model_CV,type.tun = "d")
```

# References

1. Yüzbaşı, B. and Cao, J. (2026). Collinear Groupwise Selection via Scaled Group Lasso. Accepted for publication in *The American Statistician*.
