---
title: "Start with sglasso"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Start with sglasso}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, comment="#>")
library(sglasso)
```

## From grouped predictors to predictions

`sglasso` fits penalized regression paths for user-defined, nonoverlapping
predictor groups. The grouping is an input, not an estimated clustering.
Gaussian fits predict continuous responses; binomial fits predict the
probability of the outcome coded as one.

The example below is deliberately small and synthetic. It demonstrates
the interface, not comparative performance on a research dataset.

```{r gaussian-fit}
set.seed(19)
x <- matrix(rnorm(80 * 6), 80, 6)
group <- rep(1:3, each=2)
y <- x[, 1] - x[, 3] + rnorm(80)
fit <- sglasso(x, y, group, family="gaussian",
               lambda=c(0.3, 0.1, 0.03), d=c(0, 0.5),
               alpha=0.5, screen="none")
coef(fit, lambda=0.1, d=0.5)
predict(fit, newx=x[1:3, ], lambda=0.1, d=0.5)
```

The first three training rows illustrate the prediction call. These numbers
are not out-of-sample performance estimates. For a real application, keep
test observations outside model fitting and tuning.

## Cross-validation

Use the documented `nfolds` argument and fix a seed. Alpha is fixed within
each call; use identical folds when comparing different alpha values.

```{r gaussian-cv}
set.seed(29)
cv <- cv.sglasso(x, y, group, family="gaussian",
                 lambda=c(0.3, 0.1, 0.03), d=c(0, 0.5),
                 alpha=0.5, nfolds=3, screen="none")
predict(cv, newx=x[1:3, ], s="opt")
```

This three-fold example is a documentation smoke test, not the protocol of
either article. See the study-specific run code for the original grids,
seeds, validation checks and test designs.

## Read next

- [Binary responses and CV](binomial-and-cv.html): Firth targets, fold-local
  preprocessing, probability prediction and numerical limits.
- [Data dictionary](data-dictionary.html): GenAtHum and CoRSIVSZ.
- [Example gallery](gallery.html): illustrations and completed external results.
- [Reproducing the studies](reproducibility.html): package API versus run code.

This website documents GitHub development source 1.2.0, not a tagged or CRAN
release. See the repository for the current source and the study-specific code.
